Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-26 docs/report/report.tex

\begin{document}

@@

\subsection{Related Work}
The autonomous landing problem can be thought of as a set of three separate control problems or stages. First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods. Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory. Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.

For the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor. In the work of Kim, 2014 \cite{Kim2014} a basic color thresholding technique was used to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide state estimations. In the work of Heriesse Et al. \cite{Herisse2012} an optical flow technique was applied to a series of images captured on-board the quadrotor to estimate the required states required to control the quadrotor and conduct autonomous landing. While both of these techniques have been shown to work in very specific cases both, require case specific parameters to be applied ahead of time, thereby limiting there general applicability.

In the case of Ling \cite{Kim2014}, the brightness used in his thresholding technique must be set ahead of time and is sensitive to lighting changes. A similar issue is noted in the work of Heriesse \cite{Herisse2012}. Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and, the AprilTag falling out of view of the camera during the final stages of decent. This meant that as the quadrotor approach the landing pad, it tended to lose any measurements of its state and therefore had complete the final landing procedure by propagating the last measured state forward in time.

From the controls perspective the majority of literature either uses a set of PID or a Linear Quadratic Controller (LQC) controllers to command and control the quadrotor at all stages of flight based on the state estimation provided by the techniques discussed above. An LQC was thoroughly explored in Friis Et al. \cite{Friis2009} but the authors admit even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012}, a PID controller was developed to land on a vertically oscillating platform no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
		\caption{}

	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
		\caption{}

	\end{subfigure}
	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
	\label{fig:AprilTag_eval}	
\end{figure}

@@

\subsection{PID and Controller Results}
The PID controllers derived in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system. Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted. After a signifcant amount of testing the following values for the proportional, derivative and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers. Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests. The commanded roll and pitch attitude commands produced by the PID controllers was also limited to $\pm 20^0$ for safety.

@@

From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command}, when the quadrotor is perturbed by a disturbance in teh horizontal plane, the position controller is able recover and return to the set point within 2-4 seconds. A video of flight that produced the dataset shown in \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.

@@

These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments. Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees. Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag. Such a test will be the focus of the majority of effort in the coming weeks.

@@

In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure. Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.

>>>>

\begin{document}
\raggedbottom

@@

\subsection{Related Work}
The autonomous landing problem can be thought of as a set of three separate control problems or stages. First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods. Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory. Once the quadrotor has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.

For the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor. In the work of Kim, 2014 \cite{Kim2014} a basic color thresholding technique was used to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide state estimations. In the work of Heriesse Et al., 2012 \cite{Herisse2012} an optical flow technique was applied to a series of images captured on-board the quadrotor to estimate the required states required to control the quadrotor and conduct autonomous landing. While both of these techniques have been shown to work in very specific cases both, require case specific parameters to be applied ahead of time, thereby limiting there general applicability.

In the case of Ling, 2014 \cite{Kim2014}, the brightness used in his thresholding technique must be set ahead of time and is sensitive to lighting changes. A similar issue is noted in the work of Heriesse Et al., 2012 \cite{Herisse2012}. Moreover in the work of Ling, there were implementation issues due to the slow state estimation rate of the AprilTag library and the AprilTag falling out of view of the camera during the final stages of decent. This meant that as the quadrotor approached the landing pad it tended to lose any measurements of its state and therefore had complete the final landing procedure by propagating the last measured state forward in time.

Examining the related literature on the controllers used in solving the the autonomous landing problem, the majority of literature either uses a set of PID or a Linear Quadratic Controllers (LQC) to command and control the quadrotor at all stages of flight. A LQC was thoroughly explored in Friis Et al., 2009 \cite{Friis2009} but the authors admit even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012}, a PID controller was developed to land on a vertically oscillating platform no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
		\caption{}		
	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
		\caption{}		
	\end{subfigure}
	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
	\label{fig:AprilTag_eval}	
\end{figure}

@@

\subsection{PID and Controller Results}
The PID controllers derived in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system. Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted. After a significant amount of testing the following values for the proportional, derivative and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers. Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests. The commanded roll and pitch attitude commands produced by the PID controllers was also limited to $\pm 20^0$ for safety.

@@

From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command}, when the quadrotor is perturbed by a disturbance in the horizontal plane, the position controller is able recover and return to the set point within 2-4 seconds. A video of flight that produced the dataset shown in \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.

@@

These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments. Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees. Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag.

@@

In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure. Once such a landing can be performed consistently in the face of minor disturbances, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
